---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)

books <- read_csv("data/books.csv")
```

```{r}
view(books)
```

```{r}
glimpse(books)
```

```{r}
names(books)
```


I was not interested in row or book IDs or isbn numbers.

```{r}
selected_books <- books %>% 
  select(title, authors, average_rating, language_code, num_pages, 
         ratings_count, text_reviews_count, publication_date, publisher)

selected_books
```


Checked for NAs in every column - there are none. 

```{r}
selected_books %>% 
  summarise(across(.cols = everything(), .fns = ~sum(is.na(.x))))
```


Checked how many books belong to each language code.

```{r}
selected_books %>% 
  group_by(language_code) %>% 
  summarise(language_count = n()) %>% 
  ungroup
```


I decided to only analyse books that were published in English.

```{r}
eng_books <- selected_books %>% 
  filter(language_code %in% c("eng", "en-US", "en-GB", "en-CA", "enm")) %>% 
  select(!language_code)

eng_books
```


I removed audiobooks from the data, because they usually contain 0 or a very 
small number of pages that do not match up with the physical version of the book.

```{r}
eng_books <- eng_books %>% 
  filter(!grepl("Audio", publisher)) %>% 
  filter(!grepl("Audio", title))

eng_books
```


I removed boxed sets.

```{r}
eng_books <- eng_books %>% 
  filter(!grepl("Boxed Set", title))

eng_books
```


I extracted the publication year from the publication date.

```{r}
books_year <- eng_books %>% 
  mutate(publication_year = format(as.Date(publication_date, 
                                           format = "%m/%d/%Y"), "%Y")) %>% 
  select(!publication_date)
  
books_year
```


I checked for NAs in the publication_year.

```{r}
books_year %>% 
  summarise(count = sum(is.na(publication_year)))
```


I added the correct publication year for the missing value. 

```{r}
books_year %>% 
  filter(is.na(publication_year))

books %>% 
  filter(grepl("In Pursuit of the Proper Sinner", title))

books_year <- books_year %>% 
  mutate(publication_year = coalesce(publication_year, "2000"))
```


I replaced number of pages that were 0 with the median no. of pages.

```{r}
books_year <- books_year %>% 
  mutate(num_pages = if_else(num_pages == 0, 
                             median(num_pages),
                             num_pages))
books_year
```

