---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

# MVP

## Question 1

```{r}
phone_data <- read_csv("data/20190928-items.csv") %>% 
  janitor::clean_names()
```

```{r}
glimpse(phone_data)
```

## Question 2

```{r}
phone_data %>% 
  group_by(brand) %>% 
  summarise(count = n()) %>% 
  slice_max(count, n = 1)
```

### Question 3

```{r}
samsung_mean_sd <- phone_data %>% 
  summarise(mean = mean(rating),
            sd = sd(rating))
samsung_mean_sd
```

```{r}
samsung_data <- phone_data %>% 
  filter(brand == "Samsung")

samsung_data %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..),
                 colour = "white") +
  stat_function(fun = dnorm,
                args = list(mean = samsung_mean_sd$mean, 
                            sd = samsung_mean_sd$sd),
                colour = "blue")
```

Generally the normal distribution line fits the plot quite well, but there are 
a few ratings in the centre and the ends with a really high density, that don't 
fit the normal distribution.

## Question 4

Within 1 SD

```{r}
samsung_data %>%
  filter(rating >= samsung_mean_sd$mean - samsung_mean_sd$sd,
         rating <= samsung_mean_sd$mean + samsung_mean_sd$sd) %>% 
  summarise(within_1_sd = n() / nrow(samsung_data) * 100)
```

Within 2 SD

```{r}
samsung_data %>%
  filter(rating >= samsung_mean_sd$mean - samsung_mean_sd$sd * 2,
         rating <= samsung_mean_sd$mean + samsung_mean_sd$sd * 2) %>% 
  summarise(within_2_sd = n() / nrow(samsung_data) * 100)
```

Within 3 SD

```{r}
samsung_data %>%
  filter(rating >= samsung_mean_sd$mean - samsung_mean_sd$sd * 3,
         rating <= samsung_mean_sd$mean + samsung_mean_sd$sd * 3) %>% 
  summarise(within_3_sd = n() / nrow(samsung_data) * 100)
```

The proportion of ratings within 1 sd is 77%, compared to 68% in a normal 
distribution. Within 2 sd it is 92% compared to 95% and within 3 sd it is 98% 
compared to 99.7% in the normal distribution. This shows that the ratings are
more concentrated around the mean in this data, compared to a normal 
distribution.

# Extension

```{r}
qqnorm(samsung_data$rating)
qqline(samsung_data$rating)
```

A "quantile-quantile plot" plots our data against theoretical data that has a 
normal distribution. If our data also has a normal distribution, we would expect
to see a straight line. This qq plot shows that our data is "heavy tailed",
meaning that it has more large or extreme values than data with a normal
distribution would have. 