---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(infer)
data(msleep)
```

# MVP

## 1.1 Hypothesis Testing - Practical

### Question 1

```{r}
glimpse(msleep)
```
 
### Question 2

Hypotheses:

H0: µ_sleep_total = 7
Ha: µ_sleep_total =/= 7

α = 0.05

```{r}
observed_stat <- msleep %>% 
  specify(response = sleep_total) %>% 
  calculate(stat = "mean")
observed_stat
```

```{r}
null_distribution <- msleep %>% 
  specify(response = sleep_total) %>% 
  hypothesise(null = "point", mu = 7) %>% 
  generate(reps = 10000, type = "bootstrap") %>% 
  calculate(stat = "mean")
null_distribution
```

```{r}
null_distribution %>% 
  visualise(bins = 30) +
  shade_pvalue(obs_stat = observed_stat,
               direction = "both")
```

```{r}
p_value <- null_distribution %>% 
  get_pvalue(obs_stat = observed_stat,
             direction = "both")
p_value
```

The p_value is well below the significance level of 0.05, so the null hypothesis
is successfully rejected.

This means there is enough evidence to say that the sleep_total of animals 
differs from the 7 hours of "jabberwockies".

### Question 3

Hypotheses:

H0: µ_omnivore_sleep_total - µ_herbivore_sleep_total = 0
Ha: µ_omnivore_sleep_total - µ_herbivore_sleep_total > 0

α = 0.05

```{r}
sub_msleep <- msleep %>% 
  filter(vore %in% c("omni", "herbi"))
```

```{r}
observed_stat <- sub_msleep %>% 
  specify(sleep_total ~ vore) %>% 
  calculate(stat = "diff in means",
            order = c("omni", "herbi"))
observed_stat
```

```{r}
null_distribution <- sub_msleep %>% 
  specify(sleep_total ~ vore) %>% 
  hypothesize(null = "independence") %>% 
  generate(reps = 10000, type = "permute") %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi")) 
null_distribution
```

```{r}
null_distribution %>% 
  visualise(bins = 30) +
  shade_pvalue(obs_stat = observed_stat,
               direction = "greater")
```

```{r}
p_value <- null_distribution %>% 
  get_pvalue(obs_stat = observed_stat,
             direction = "greater")
p_value
```

The p_value is much greater than our level of significance of 0.05, so the null 
hypothesis cannot be rejected. 

This means there is not enough evidence to say that on average omnivores sleep 
for significantly longer than herbivores.

### Question 4

Hypotheses:

H0: π_is_domesticated = 5%
Ha: π_is_domesticated > 5%

α = 0.05

```{r}
msleep_domesticated <- msleep %>% 
  mutate(is_domesticated = (conservation == "domesticated"),
# Replaced missing values with FALSE, because none were domesticated animals
         is_domesticated = coalesce(is_domesticated, FALSE))
```

```{r}
observed_stat <- msleep_domesticated %>% 
  specify(response = is_domesticated, success = "TRUE") %>% 
  calculate(stat = "prop")
observed_stat
```

```{r}
null_distribution <- msleep_domesticated %>% 
  specify(response = is_domesticated, success = "TRUE") %>% 
  hypothesise(null = "point", p = 0.05) %>% 
  generate(reps = 10000, type = "draw") %>% 
  calculate(stat = "prop")
```

```{r}
null_distribution %>% 
  visualise(bins = 10) +
  shade_pvalue(obs_stat = observed_stat,
               direction = "greater")
```

```{r}
p_value <- null_distribution %>% 
  get_pvalue(obs_stat = observed_stat,
             direction = "greater")
p_value
```

The p_value is smaller than the significance level, which means the null 
hypothesis can be rejected. 

The proportion of domesticated animal types in the population of animal types is
greater than 5%.

## 1.2 Hypothesis Testing - Defining the Hypothesis

### Question 1

Test:

I would use the single-sample proportion hypothesis test, using the "draw" 
method to generate the null distribution.

Hypotheses:

Null hypothesis: 40% of people in the town have heard of the coffee shop.
Alternative hypothesis: The number of people in the town that have heard of the 
coffee shop is greater than 40%

H0: π_aware_of_shop = 40%
Ha: π_aware_of_shop > 40%

### Question 2

Test:

I would use an independent two-sample hypothesis test, using the "permutation"
method to generate the null distribution

Hypotheses:

Null hypothesis: The CTR rate is the same regardless of where the banner is 
positioned.
Alternative hypothesis: The CTR rate is higher if banner is positioned at the
top of the page.

H0: ctr_group_b - ctr_group_a = 0
Ha: ctr_group_b - ctr_group_a > 0

### Question 3

Test:

I would use the single-sample mean hypothesis test, using the "bootstrap" method
to generate the null distribution.

Hypotheses:

Null hypothesis: The manufacturing process has not drifted, and the mean width 
of the part is 145mm.
Alternative hypothesis: The mean width of parts differs significantly from 145mm
i.e. the manufacturing process has drifted.

H0: µ_width = 145
Ha: µ_width =/= 145
