---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(ggfortify)
```

# MVP

```{r}
project <- read_csv("data/project_management.csv")
```

```{r}
project %>% 
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point()
```

```{r}
project %>% 
  summarise(cor(estimated_length, actual_length))
```

A correlation coefficient of 0.8 means that the variables are very strongly
positively correlated.

```{r}
model <- lm(actual_length ~ estimated_length,
            data = project)
summary(model)
```

The `estimated_length` regression coefficient is 1.2235. This means that for 
every day the `estimated_length` increases, the `actual_length` increases by 
1.2235 days. 

The r-squared is 0.65. This means that 65% of the variation in the 
`actual_length` can be explained by variation in `estimated_length`.

```{r}
autoplot(model)
```

The diagnostic plots seem to satisfy the 3 required residual conditions:

There is no distinguishable pattern in Residuals vs Fitted plot, which means 
the residuals are independent of each other.

The residuals seem to be normally distributed apart from one large outlier. 

The line in the Scale-Location plot is fairly constant, which means there is 
no systematic variation in residual size. 

Having satisfied these conditions, and a p-value < 0.001, we can conclude that 
the relationship is statistically significant.