---
title: "R Notebook"
output: html_notebook
---

```{r}
library(rpart)
library(rpart.plot)
library(tidyverse)
library(modelr)
library(caret)

titanic_set <- read_csv('data/titanic_decision_tree_data.csv')

shuffle_index <- sample(1:nrow(titanic_set))

# shuffle the data so class order isn't in order - need this for training/testing split later on 
titanic_set <- titanic_set[shuffle_index, ]
```

# MVP

## Question 1

```{r}
titanic_set_tidy <- titanic_set %>% 
  janitor::clean_names() %>% 
  filter(!is.na(survived)) %>% 
  mutate(sex = as.factor(sex),
         age_status = as.factor(if_else(age <= 16, "child", "adult")),
         class = factor(pclass, 
                        levels = c(1, 2, 3), 
                        labels = c("upper", "middle", "lower")),
         port_embarkation = as.factor(embarked),
         survived_flag = factor(survived,
                                levels = c(0, 1),
                                labels = c("no", "yes"))) %>% 
  select(sex, age_status, class, port_embarkation, 
         sib_sp, parch, survived_flag) %>% 
  drop_na()
```

## Question 2

```{r}
GGally::ggpairs(titanic_set_tidy)
```

Seems like sex and class might be useful in predicting whether a passenger is
going to die. 

## Question 3

I chose an 80/20 split, since there are not that many observations in the dataset.

```{r eval=FALSE}
n_data <- nrow(titanic_set_tidy)

test_index <- sample(1:n_data, size = n_data * 0.2)

titanic_test <- slice(titanic_set_tidy, test_index)
titanic_train <- slice(titanic_set_tidy, -test_index)
```

```{r eval=FALSE}
titanic_test %>%
  janitor::tabyl(survived_flag)

titanic_train %>% 
  janitor::tabyl(survived_flag)
```

```{r}
titanic_sample <- 
  splitstackshape::stratified(titanic_set_tidy,
                              group = "survived_flag",
                              size = 0.2,
                              bothSets = TRUE)
```

```{r}
titanic_test <- titanic_sample$SAMP1
titanic_train <- titanic_sample$SAMP2
```

```{r}
titanic_test %>%
  janitor::tabyl(survived_flag)

titanic_train %>% 
  janitor::tabyl(survived_flag)
```

# Question 4

```{r}
titanic_fit <- rpart(survived_flag ~ .,
                     data = titanic_train,
                     method = "class")
```

```{r}
rpart.plot(titanic_fit,
           yesno = 2,
           fallen.leaves = TRUE)
```

# Question 5

So, I don't know what I did wrong, but it's attaching 0.4 to the "no" category
in the root node, even though it should be 0.6. Then, it appears that the rest 
of the tree map is based on `survived_flag == "yes"` being the majority because 
it is saying that females have a 75% chance of dying, which makes no sense. 

So, ignoring these, the map is telling us that males have only 0.2 chance of 
survival, while for females it's 0.77. Females that are not in the lower class
have a 0.95 chance of surviving, while females in the lower class have a 0.47
chance of surviving. Then, females in the lower class that have one or more 
siblings or spouses have a 0.34 chance of surviving and ones that have none have
a 0.60 chance of surviving.

The important variables in this tree map are sex, class and sib_sp. 

# Question 6

```{r}
titanic_test_pred <- titanic_test %>% 
  add_predictions(titanic_fit, type = "class")
```

```{r}
confusionMatrix(titanic_test_pred$pred,
                titanic_test_pred$survived_flag)
```

This tells us that this decision tree correctly predicts 74 positives and 33
negatives which places the model's accuracy at 75%.
There are also 11 false positives and 25 false negatives.

In terms of this dataset, the model correctly predicted the 74 people that 
didn't survive, and 33 people that did. It also incorrectly predicted the 
survival of 11 people and the death of 25.