---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(CodeClanData)
```

# MVP

## Question 1

```{r}
glimpse(backpack)
```

## Question 2

```{r}
ggplot(backpack,
       aes(x = backpack_weight)) +
  geom_bar(fill = "Steelblue") +
  labs(x = "\nBackpack Weight (lb)",
       y = "Frequency\n",
       title = "Backpack Weights of Students\n") +
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12)) +
  scale_x_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30, 35)) +
  theme_minimal()
```

In this data, the backpack weight that occurs most frequently is 10lb. The most 
common backpack weights range from around 5lb to 15lb. There are very few 
backpack weights that are below 5lb or above 20lb.

## Question 3

```{r}
ggplot(backpack,
       aes(x = backpack_weight, fill = sex)) +
  geom_bar(show.legend = FALSE) +
  facet_wrap(~ sex) +
  labs(x = "\nBackpack Weight (lb)",
       y = "Frequency\n",
       title = "Backpack Weights of Students\n") +
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12)) +
  scale_x_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30, 35)) +
  theme_minimal() +
  theme(strip.text = element_text(size = 11),
        plot.title = element_text(hjust = 0.45))
```

The general backpack distribution is very similar for both sexes. The 
most common backpack weight for females is 10lb and 11lb for males. 

## Question 4

```{r}
ggplot(backpack,
       aes(x = body_weight, y = backpack_weight)) +
  geom_point(colour = "Steelblue") +
  labs(
    x = "\nBody Weight (lb)",
    y = "Backpack Weight (lb)\n",
    title = "Students' Body Weight vs Backpack Weight\n"
  ) +
  theme_minimal()
```

There does not seem to be a clear relationship between students' body weight and
their backpack weight.

## Question 5

```{r}
ggplot(backpack,
       aes(x = body_weight, y = backpack_weight, colour = sex)) +
  geom_point() +
  labs(
    x = "\nBody Weight (lb)",
    y = "Backpack Weight (lb)\n",
    colour = "Sex",
    title = "Students' Body Weight vs Backpack Weight\n"
  ) +
  theme_minimal()
```

Again, there appears to be no distinguishable relationship between backpack and 
body weights of student males or females.

## Question 6

```{r}
backpack %>% 
  mutate(back_problems = as.logical(back_problems)) %>% 
  group_by(back_problems) %>% 
  mutate(count = n()) %>% 
  
ggplot(aes(1, fill = back_problems)) +
  geom_bar(position = "stack") +
  geom_text(aes(y = count/5, label = count),
            colour = "white", vjust = -6.5) +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  labs(fill = "Back Problems",
       title = "Proportion of Students With Back Pain")
```

In this data set 32% of students have reported back pain.


```{r}
backpack %>% 
  mutate(back_problems = as.logical(back_problems)) %>% 
  group_by(back_problems, sex) %>% 
  mutate(count = n()) %>% 
  
ggplot(aes(x = sex, fill = back_problems)) +
  geom_bar(position = "fill") +
  geom_text(aes(y = count/100, label = count),
            colour = "white") +
  labs(fill = "Back Problems",
       title = "Proportion of Students With Back Pain") +
  theme_minimal() +
  theme(axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(hjust = 0.5))
```

44% of females report back pain, and only 18% of males.