---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(factoextra)
library(broom)
```

```{r}
mall_customers <- read_csv("data/mall_customers.csv")
```

```{r}
summary(customers_clean)
```

There are no NAs in the dataset.

```{r}
customers_clean <- mall_customers %>% 
  janitor::clean_names() %>% 
  rename(spending_score = spending_score_1_100) %>% 
  select(-customer_id)
```

```{r}
GGally::ggpairs(customers_clean)
```

There appear to be clusters in `annual_income_k` vs `spending_score` plot. 
There appear to be clusters in `age` vs `spending_score` plot.

--------------------------------------------------------------------------------

```{r}
customers_scaled <- customers_clean %>% 
  select(-gender, -age) %>% 
  mutate_all(scale)
```

```{r}
max_k <- 20

K_cluster_customers <- tibble(k = 1:max_k) %>% 
  mutate(kclust = map(k, ~kmeans(customers_scaled, .x, nstart = 25)))
```

```{r}
fviz_nbclust(customers_scaled,
             kmeans,
             method = "wss",
             nstart = 25)

fviz_nbclust(customers_scaled,
             kmeans,
             method = "silhouette",
             nstart = 25)

fviz_nbclust(customers_scaled,
             kmeans, 
             method = "gap_stat")
```

Choose k = 5 

```{r}
clusters_k5 <- kmeans(customers_scaled,
                      centers = 5,
                      nstart = 25)
```

```{r}
augment(clusters_k5, customers_scaled) %>% 
  ggplot(aes(x = annual_income_k, 
             y = spending_score,
             colour = .cluster)) +
  geom_point()
```

Based on the optimal clusters plots, there was no clear optimal number of 
clusters for this dataset. However, based on this visualisation, the clustering 
seems to be a really good fit for this data.

Cluster 1 - high income, low spenders
Cluster 2 - low income, high spenders
Cluster 3 - mid income, mid spenders
Cluster 4 - high income, high spenders
Cluster 5 - low income, low spenders

```{r}
tidy(clusters_k5) %>% 
  select(cluster, size)
```

Important to note that cluster 3 (mid income, mid spenders) is by far the 
largest cluster, with clusters 2 and 5 being quite small in comparison.