---
title: "R Notebook"
output: html_notebook
---

--- Load in packages and data
```{r}
library(tidyverse)

movies <- read_csv("data/movies.csv")
```

--- Question 1

```{r}
dim(movies)
```
```{r}
str(movies)
```


The names of the columns seem to be appropriate so I would leave those as they are.

There are NAs and 0 values in certain columns. I could find out how many NAs there are and in which columns.
Then I could decide the appropriate action to take with regards to the NAs, e.g. ignore or replace.

Depending on which variables I need, I can also decide what to do with values that are 0.

I could change the variables in budget and revenue to make them more readable and easier to compare.

Then I could also sort the data by certain variables, e.g. vote_average, revenue, popularity etc.

I could also group the original_language column to explore data about movies depending on their original language.

I could find out which movies are the most and least popular, which ones have the highest rating or budget etc.


--- Question 2

```{r}
movies_selected <- movies %>% 
  select(title, runtime, budget) 
```

I selected title instead of original_title because there are different languages in original_title,
so to make it easier to read and understand the data, I want all of them to be in English.

--- Question 3

```{r}
movies_selected %>%
  summarise(na_count_title = sum(is.na(title)),
            na_count_runtime = sum(is.na(runtime)),
            na_count_budget = sum(is.na(budget)))
```

There are 2 missing values in runtime.

--- Question 4

```{r}
movies_runtime <- movies_selected %>%
  mutate(runtime = na_if(runtime, 0)) 

movies_runtime %>% 
  summarise(na_count_runtime = sum(is.na(runtime)))
```

There are now 37 missing values in runtime.

--- Question 5

```{r}
movies_imputed <- movies_runtime %>%
  mutate(runtime = coalesce(runtime, median(runtime, na.rm = TRUE)))

movies_imputed %>%
  summarise(na_count_runtime = sum(is.na(runtime)))
```
There are now 0 missing values in runtime.

--- Question 6

Movies with shortest runtime:

```{r}
movies_imputed %>%
  slice_min(runtime, n = 10)
```

Movies with longest runtime:

```{r}
movies_imputed %>% 
  slice_max(runtime, n = 10)
```

--- Question 7

```{r}
movies_imputed <- movies_imputed %>% 
  mutate(budget = if_else(budget < 100, # if budget is below 100
                          median(budget), # it will be replaced by the median of budget
                          budget)) # else, the value stays the same

movies_imputed
```

--- Extension Question 1

```{r}
movie_budgets <- movies_imputed %>% 
  mutate(budget_type = case_when(
    budget < 12e6 ~ "Small budget", 
    budget >= 12e6 & budget < 40e6 ~ "Medium budget",
    budget >= 40e6 ~ "Big budget"
  ))

movie_budgets
```

--- Extension Question 2

Number of NAs in character columns

```{r}
movies %>% 
  summarise(across(where(is.character), ~sum(is.na(.))))
```

Number of NAs in numerical columns

```{r}
movies %>% 
  summarise(across(where(is.numeric), ~sum(is.na(.))))
```
