---
title: "R Notebook"
output: html_notebook
---
--- Load in libraries

```{r}
library(tidyverse)
library(CodeClanData)
```

--- Question 1

Get dimensions of drinks_content

```{r}
dim(drinks_content)
```

Get the structure of drinks_content

```{r}
str(drinks_content)
```

--- Question 2

Select columns 'Beverage_category', 'Beverage', 'Beverage_prep' and 'Calories' from the data

```{r}
drinks_cal <- select(drinks_content, Beverage_category, Beverage, Beverage_prep, Calories)
```

Check the amount of NAs in column 'Calories'

```{r}
which(is.na(drinks_cal$Calories))
```

There are no NAs in column 'Calories'

--- Question 3

Create a new variable calorie_diff 

```{r}
mutate(drinks_cal, calorie_diff = Calories - 135)
```

--- Question 4

Group categories in column 'Beverage_category'

```{r}
grouped_beverages <- group_by(drinks_cal, Beverage_category)
```

Summarise the mean no. of calories in each beverage category

```{r}
mean_categories <- summarise(grouped_beverages, mean_calories = mean(Calories))
```

Arrange mean calories in descending order

```{r}
sorted_mean_categories <- arrange(mean_categories, desc(mean_calories))
```

Find 3 categories of drinks with most calories

```{r}
head(sorted_mean_categories, 3)
```

Find 3 categories of drinks with least amount of calories

```{r}
tail(sorted_mean_categories, 3)
```

The 3 categories of beverages with the most calories are Smoothies,	Frappuccino® Blended Coffee and Signature Espresso Drinks.
The 3 categories of beverages with the least amount of calories are Classic Espresso Drinks, Shaken Iced Beverages and Coffee.

--- Question 5

Group categories in column 'Beverage_prep'

```{r}
grouped_prep <- group_by(drinks_cal, Beverage_prep)
```

Calculate mean no. of calories for each prep type

```{r}
prep_cal_summary <- summarise(grouped_prep, mean_cal_prep = mean(Calories))
prep_cal_summary
```

--- Question 6

Calculate average calories of all beverages

```{r}
mean_all <- mean(drinks_content$Calories)
```

Find out which types of beverage prep contain more calories than the average

```{r}
filter(prep_cal_summary, mean_cal_prep > mean_all)
```

--- Question 7

```{r}
drinks_cal %>% 
  filter(Beverage_category == "Coffee") %>%  # only includes rows where Coffee is the beverage category
  arrange(Calories) %>% # orders the 'calories' values in ascending order, so the lowest calorie value is at the top
  head(1) # returns the top row
```

The Coffee type with the least amount of calories is short.