---
title: "R Notebook"
output: html_notebook
---

# MVP

## 1.1 The Titanic

```{r}
library(prob)
library(gtools)
library(tidyverse)
```

```{r}
titanic <- read_csv("data/titanic.csv")
```

```{r}
titanic <- titanic %>% 
  mutate(crew = if_else(str_detect(class, "crew") | 
                          str_detect(class, "staff"),
                        TRUE,
                        FALSE))
```

prob(survived | crew)

```{r}
prob_crew <- titanic %>%
  summarise(prob = sum(crew == TRUE) / n())
prob_crew
```

```{r}
prob_survived_crew <- titanic %>%
  filter(crew == TRUE, survived == "yes") %>% 
  summarise(prob = n() / nrow(titanic))
prob_survived_crew
```

```{r}
prob_survived_given_crew = prob_survived_crew / prob_crew
prob_survived_given_crew
```

prob(survived | passenger)

```{r}
prob_passenger <- titanic %>%
  summarise(prob = sum(crew == FALSE) / n())
prob_passenger
```

```{r}
prob_survived_passenger <- titanic %>%
  filter(crew == FALSE, survived == "yes") %>% 
  summarise(prob = n() / nrow(titanic))
prob_survived_passenger
```

```{r}
prob_survived_given_passenger = prob_survived_passenger / prob_passenger
prob_survived_given_passenger
```

The probability of surviving given you were part of the crew = 0.237 OR 24%
The probability of surviving given you were a passenger = 0.380 OR 38%
This means that the passengers of Titanic were more likely to survive than the 
crew.

## 1.2 Probability Consolidation Questions

### Question 1

```{r}
s_one_die <- rolldie(1)
prob_one_die <- s_one_die %>% 
  summarise(prob = sum(X1 < 5) / n())
prob_one_die
```

The probability of rolling less than 5 is 0.666667 OR 2/3

### Question 2

```{r}
s_three_dice <- rolldie(3) %>% 
  nrow()
s_three_dice
```

OR 

```{r}
s_three_dice <- 6^3
s_three_dice
```

There are 216 outcomes.

### Question 3

i.

```{r}
s_four_dice <- rolldie(4)
se_total_5_6_7 <- s_four_dice %>% 
  filter((X1 + X2 + X3 + X4) %in% c(5, 6, 7)) %>% 
  summarise(outcomes = n())
se_total_5_6_7
```

ii. 

```{r}
prob_total_5_6_7 <- se_total_5_6_7 %>% 
  summarise(prob = se_total_5_6_7 %>% pull() / nrow(s_four_dice))
prob_total_5_6_7
```

iii. 

The assumption is that every sample point is as likely as another.

### Question 4

```{r}
s_heights <- as.tibble(permutations(n = 5, r = 5, repeats.allowed = FALSE))

prob_desc_heights <- 1 / nrow(s_heights)
prob_desc_heights
```

### Question 5

i.

```{r}
s_six_dice_perm <- as.tibble(permutations(n = 6, r = 6, repeats.allowed = TRUE))

prob_desc_six_dice <- 1 / nrow(s_six_dice_perm)
format(prob_desc_six_dice, scientific = F)
```

ii.

```{r}
s_six_dice_comb <- as.tibble(combinations(n = 6, r = 6, repeats.allowed = TRUE))

prob_each_num_six_dice <- 1 / nrow(s_six_dice_comb)
prob_each_num_six_dice
```

