---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(infer)
```

# MVP

## Task 1

```{r}
ames <- read_csv("data/ames.csv") %>%
  clean_names()
```

```{r}
glimpse(ames)
```

## Task 2

```{r}
ames %>% 
  ggplot(aes(x = lot_area)) +
  geom_histogram()
```

The distribution is right skewed. 

## Task 3

```{r}
bootstrap_resample <- ames %>% 
  specify(response = lot_area) %>% 
  generate(reps = 10000, type = "bootstrap") %>% 
  calculate(stat = "mean")
```

```{r}
bootstrap_resample %>% 
  visualise(bins = 30)
```

## Task 4

```{r}
ci_95 <- bootstrap_resample %>% 
  get_ci(level = 0.95, type = "percentile")
ci_95
```

```{r}
bootstrap_resample %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = ci_95)
```

## Task 5

```{r}
ci_99 <- bootstrap_resample %>% 
  get_ci(level = 0.99, type = "percentile")
ci_99
```

```{r}
bootstrap_resample %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = ci_99)
```

The 99% CI is broader than the 95% CI. This makes sense because to decrease 
uncertainty, you have to increase your range of possible values.

## Task 6

```{r}
bootstrap_resample %>% 
  summarise(point_estimate = mean(stat))
```

# Extension

## Task 1

```{r}
ames_1920 <- ames %>% 
  mutate(before_1920 = if_else(year_built < 1920,
                               TRUE,
                               FALSE))
ames_1920
```

200 reps

```{r}
bootstrap_resample_1920 <- ames_1920 %>% 
  specify(response = before_1920, success = "TRUE") %>% 
  generate(reps = 200, type = "bootstrap") %>% 
  calculate(stat = "prop")

ci_95_1920 <- bootstrap_resample_1920 %>% 
  get_ci(level = 0.95, type = "percentile")
ci_95_1920

bootstrap_resample_1920 %>% 
  summarise(point_estimate = mean(stat))

ci_95_1920$upper_ci - ci_95_1920$lower_ci
```

1000 reps

```{r}
bootstrap_resample_1920 <- ames_1920 %>% 
  specify(response = before_1920, success = "TRUE") %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "prop")

ci_95_1920 <- bootstrap_resample_1920 %>% 
  get_ci(level = 0.95, type = "percentile")
ci_95_1920

bootstrap_resample_1920 %>% 
  summarise(point_estimate = mean(stat))

ci_95_1920$upper_ci - ci_95_1920$lower_ci
```

5000 reps

```{r}
bootstrap_resample_1920 <- ames_1920 %>% 
  specify(response = before_1920, success = "TRUE") %>%
  generate(reps = 5000, type = "bootstrap") %>% 
  calculate(stat = "prop")

ci_95_1920 <- bootstrap_resample_1920 %>% 
  get_ci(level = 0.95, type = "percentile")
ci_95_1920

bootstrap_resample_1920 %>% 
  summarise(point_estimate = mean(stat))

ci_95_1920$upper_ci - ci_95_1920$lower_ci
```

10000 reps

```{r}
bootstrap_resample_1920 <- ames_1920 %>% 
  specify(response = before_1920, success = "TRUE") %>%
  generate(reps = 10000, type = "bootstrap") %>% 
  calculate(stat = "prop")

ci_95_1920 <- bootstrap_resample_1920 %>% 
  get_ci(level = 0.95, type = "percentile")
ci_95_1920

bootstrap_resample_1920 %>% 
  summarise(point_estimate = mean(stat))

ci_95_1920$upper_ci - ci_95_1920$lower_ci
```

25000 reps

```{r}
bootstrap_resample_1920 <- ames_1920 %>% 
  specify(response = before_1920, success = "TRUE") %>%
  generate(reps = 25000, type = "bootstrap") %>% 
  calculate(stat = "prop")

ci_95_1920 <- bootstrap_resample_1920 %>% 
  get_ci(level = 0.95, type = "percentile")
ci_95_1920

bootstrap_resample_1920 %>% 
  summarise(point_estimate = mean(stat))

ci_95_1920$upper_ci - ci_95_1920$lower_ci
```

50000 reps

```{r}
bootstrap_resample_1920 <- ames_1920 %>% 
  specify(response = before_1920, success = "TRUE") %>%
  generate(reps = 50000, type = "bootstrap") %>% 
  calculate(stat = "prop")

ci_95_1920 <- bootstrap_resample_1920 %>% 
  get_ci(level = 0.95, type = "percentile")
ci_95_1920

bootstrap_resample_1920 %>% 
  summarise(point_estimate = mean(stat))

ci_95_1920$upper_ci - ci_95_1920$lower_ci
```

The number of reps used certainly matters. Using only 200 reps, the CI varies
quite significantly. The more reps used, the more consistent the CI and the 
point estimate. Although 25,000 and 50,000 reps produce virtually the same 
results as 10'000 reps, so there is no need to go that high.
